---
title: "p8105_hw5_wz2590"
author: "Weiheng Zhang"
date: "2021/11/11"
output: github_document
---

```{r message = FALSE}
library(tidyverse)
library(dplyr)
library(patchwork)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1, following the instructions in the office hour.

We will analyze the data published by  _The Washington Post_ on homicides in 50 large U.S. cities. 

```{r warning=FALSE, message=FALSE}
homicide_df = 
  read_csv("./data/Problem1/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved",
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Let's focus on Baltimore, MD.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summmary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
    x = baltimore_summmary %>% pull(unsolved), 
    n = baltimore_summmary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

Let's try to iterate across cities!
Firstly, write a function and test it on a few sample cities.

```{r}
prop_test_function = function(city_df){
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
      )
  
  return(city_test)
  
}

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Now, let's iterate across all cities,

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Try to make a plot showing estimates and confidence intervals.

```{r dpi = 300}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

An alternative way for problem 1:

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```



## Problem 2

Use iteration to read in the data files and do some data cleaning.
```{r message=FALSE, warning=FALSE}
longitudinal_df = 
  tibble(
    path = list.files("data/Problem2")) %>% 
  mutate(
    path = str_c("data/Problem2/", path),
    data = map(path, read_csv)) %>% 
  separate(path, c(NA, NA,"name"), sep = "/") %>% 
  separate(name, c("Arm","Subject_ID", NA)) %>% 
  mutate(Arm = recode(Arm, con = "Control", exp = "Experiment")) %>% 
  unnest(data)
longitudinal_df
```
convert to long format for graphing in the next step.
```{r}
longitudinal_long = longitudinal_df %>% 
  pivot_longer(week_1:week_8,
               names_prefix = "week_",
               names_to = "Week",
               values_to = "Observation") %>% 
  mutate(Week = as.numeric(Week))

longitudinal_long
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r dpi=300}
longitudinal_long %>% 
  ggplot(aes(x = Week, y = Observation, group = Subject_ID, color = Subject_ID)) +
  geom_line(size = 0.8) + 
  geom_point() +
  labs(
    title = "Observations of Subjects in Control and Experiment Groups Over Time",
    x = "Weeks",
    y = "Observation",
    color = "Subject ID of Correspounding Group"
  ) +
  facet_grid(. ~ Arm)
```
Generally, the observations of each subject in the experimental group increases over time, while subjects in the control group does not show clear association between time and observation. Overall, observations of subjects in the experimental group are higher than observations of subjects in the control group, during the study period.  
  
  
## Problem 3
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing
```


Write a function that takes a vector as an argument; replaces missing values using the rules defined; and returns the resulting vector. 
Apply this function to the columns of iris_with_missing using a map statement.
```{r}
iris_fill = function(vec) {
  length = length(vec)
  
  if (is.numeric(vec)) {
    mean = mean(vec, na.rm = T) %>% 
      round(digits = 1)
    for (i in 1:length) {
      if (is.na(vec[i])) {
        vec[i] = mean
      }
    }
  }
  
  else if (is.character(vec)) {
    for (i in 1:length) {
      if (is.na(vec[i])) {
        vec[i] = "virginica"
      }
    }
  }
  
  return(vec)
  
}

results = map(iris_with_missing, iris_fill)
as_tibble(results) %>% 
  knitr::kable()
```












